Liveness-Based Garbage Collection for Lazy Languages

### 2015-04-07 paper/paper.tex
Committing minor changes

\section{Generating Liveness Equations}
\begin{figure*}[t!]
%%\begin{picture}(100,130)(0,-90)
\begin{picture}(100,130)(0, -50)
  \begin{tabular}{cc}
    \begin{boxedminipage}{.51\textwidth}
      {\sf
        \small
        \renewcommand{\arraystretch}{1}{
          \begin{uprogram}
            \UNL{1} (\DEFINE\ (\length~\xl)
            \UNL{2}  $\pi_1\!\!:\, $(\LET\ \px\ $\leftarrow $\ (\NULLQ~\xl) \IN
            \UNL{3} \hspace*{.05cm} $\pi_2\!\!:\,$(\SIF$_{ep_3}$\ $\pi_3\!\!:\,$ \px
            \UNL{4} \hspace*{1.15cm} $\pi_4\!\!:\, (\RETURN_{ep_1}~0)$
            \UNL{4} \hspace*{1.15cm}    $\pi_5\!\!:\, $(\LET~\pu\  $\leftarrow$  (\CDR~\xl)  \IN
            \UNL{5} \hspace*{1.15cm}   $\pi_6\!\!:\, $(\LET~\py\  $\leftarrow$  (\length~\pu)  \IN
            \UNL{6} \hspace*{1.15cm} $\pi_7\!\!:\, (\RETURN_{ep_2}~(1~+~\py))$)))))
        \end{uprogram}}
        \renewcommand{\arraystretch}{1}{
	  \begin{uprogram}
	  \UNL{1} $\pi_\mainpgm\!\!:\, \pi_8\!\!:\, $(\LET\  \pa\  $\leftarrow$ \ldots  \IN
	  \UNL{2}   \hspace*{.78cm}   $\pi_9\!\!:\,      $ (\LET\ \pb\  $\leftarrow$  \ldots \IN 
          \UNL{3}   \hspace*{.78cm}    $\pi_{10}\!\!:\, $(\LET\ \pw\  $\leftarrow$  (\length\ \pb) \IN~$\pi_{11}\!\!:\,$ (\RETURN$_{ep_4}$\ \pw)))))))
\end{uprogram}}
        } 
    \end{boxedminipage}
    & 
    \begin{boxedminipage}{.49\textwidth}
      {\sf
        \small
        \begin{tabular}{lc}
        $\cal{M_{\mbox{\tiny length}}} = $ 
            \begin{tabular}{lc}            
              $[$
              $ep_2 \mapsto \lbrace \py.\epsilon, \pu.\Lf{\length}{\mbox{1}}{\epsilon}, \
              \xl.\mbox{1}\Lf{\length}{\acdr}{\epsilon}, \xl.\epsilon  \rbrace ,$ \\ 
              $ep_1 \mapsto \lbrace \rbrace , $\\
              $ep_3 \mapsto \lbrace \px.\epsilon, \xl.\epsilon \rbrace $  \\
              $]$
            \end{tabular} \\
            $\cal{P_{\mbox{\tiny length}}} = [$
              \begin{tabular}{lc}
                $\pi_{\mbox{1}} \mapsto \lbrace ep_1, ep_2, ep_3 \rbrace, $ \
                $ \pi_{\mbox{2}} \mapsto \lbrace ep_1, ep_2, ep_3 \rbrace, $ \\
                $ \pi_{\mbox{3}} \mapsto \lbrace ep_3 \rbrace, $ \
                $ \pi_{\mbox{4}} \mapsto \lbrace ep_1 \rbrace, $ \
                $ \pi_{\mbox{5}} \mapsto \lbrace ep_2 \rbrace, $ \\
                $ \pi_{\mbox{6}} \mapsto \lbrace ep_2 \rbrace, $ \
                $ \pi_{\mbox{7}} \mapsto \lbrace ep_2 \rbrace $ \\
                $]$
              \end{tabular}\\
              $\cal{M_{\mbox{\tiny main}}} = $ 
              \begin{tabular}{lc}            
                $[$
                  $ep_4 \mapsto \lbrace \pw.\sigma_{\mathit{\!all}}, \pb.\Lf{\length}{\mbox{1}}{\sigma_{\mathit{\!all}}}, \ldots  \rbrace $ \
                  $]$
              \end{tabular} \\
              $\cal{P_{\mbox{\tiny main}}} = [$
                \begin{tabular}{lc}
                  $\pi_{\mbox{8}} \mapsto \lbrace ep_4 \rbrace, $ \
                  $ \pi_{\mbox{9}} \mapsto \lbrace ep_4 \rbrace, $ \\
                  $ \pi_{\mbox{10}} \mapsto \lbrace ep_4 \rbrace, $ \
                  $ \pi_{\mbox{11}} \mapsto \lbrace ep_4 \rbrace, $ \
                  $ \ldots  $ \
                  $]$  
                \end{tabular}
        \end{tabular}
      }
    \end{boxedminipage}
    \\
    (a) Example program.&
    \renewcommand{\arraystretch}{.9}{\begin{tabular}[t]{ll}
        (b) {\em e-path} to liveness environment map \\
        (c) Prog pt to {\em e-paths } map
    \end{tabular}}
  \end{tabular}
\end{picture}
\kern -3ex
\vspace{0.5in}
\caption{Example Program and its liveness maps.}\label{fig:mot-example2}    
\end{figure*}

@@

  \raggedright{\bf Steps:}
 \begin{algorithmic}
   \STATE $i \leftarrow 0$ 
   \STATE $\nt_0 \leftarrow$ Equivalent NFA of \ntbar\
   without $\epsilon$-moves \cite{hopcraft90toc}

   \REPEAT
   \STATE $\nt'_{i+1} \leftarrow \nt_i$
   \FORALL{states $q$ in $\nt_i$ such that $q$ has an incoming
     edge from $q'$ with label $\bcar$ and
     outgoing edge to $q''$ with label $\acar$} 
   \STATE add an edge in $\nt'_{i+1}$ from $q'$ to $q''$ with
   label $\epsilon$.
   \COMMENT{bypass  $\bcar\acar$ using $\epsilon$}
   \ENDFOR

   \FORALL{states $q$ in $\nt_i$ such that $q$ has an incoming
     edge from $q'$ with label $\bcdr$ and outgoing edge to
     $q''$ with label $\acdr$} 
   \STATE add an edge in $\nt'_{i+1}$ from $q'$ to $q''$ with
     label $\epsilon$.
   \COMMENT{bypass  $\bcdr\acdr$ using $\epsilon$}
   \ENDFOR

   \STATE   $\nt_{i+1}    \leftarrow$   Equivalent   NFA   of
   $\nt'_{i+1}$ without $\epsilon$-moves

   \STATE $i \leftarrow i+1$
   \UNTIL ($\nt_{i} = \nt_{i-1}$)

   \STATE $\nt \leftarrow \nt_i$
%   \STATE delete all edges with label \bcar\ or \bcdr\ in \nt.
 \end{algorithmic}
\end{center}
\end{boxedminipage}
 \caption{Algorithm for transforming an NFA to  accept forward
   paths only.}\label{algo:simplify-NFA} \figrule
\end{figure*}

>>>>

\section{Generating Liveness Equations}
\begin{figure*}[t!]
%%\begin{picture}(100,130)(0,-90)
\begin{picture}(100,130)(0, -50)
  \begin{tabular}{cc}
    \begin{boxedminipage}{.51\textwidth}
      {\sf
        \small
        \renewcommand{\arraystretch}{1}{
          \begin{uprogram}
            \UNL{1} (\DEFINE\ (\length~\xl)
            \UNL{2}  $\pi_1\!\!:\, $(\LET\ \px\ $\leftarrow $\ (\NULLQ~\xl) \IN
            \UNL{3} \hspace*{.05cm} $\pi_2\!\!:\,$(\SIF\ $\psi_3\!\!:\,$ \px
            \UNL{4} \hspace*{1.15cm} $\psi_1\!\!:\, (\RETURN~0)$
            \UNL{4} \hspace*{1.15cm}    $\pi_3\!\!:\, $(\LET~\pu\  $\leftarrow$  (\CDR~\xl)  \IN
            \UNL{5} \hspace*{1.15cm}   $\pi_4\!\!:\, $(\LET~\py\  $\leftarrow$  (\length~\pu)  \IN
            \UNL{6} \hspace*{1.15cm} $\psi_2\!\!:\, (\RETURN~(1~+~\py))$)))))
        \end{uprogram}}
        \renewcommand{\arraystretch}{1}{
	  \begin{uprogram}
	  \UNL{1} $\pi_\mainpgm\!\!:\, \pi_5\!\!:\, $(\LET\  \pa\  $\leftarrow$ \ldots  \IN
	  \UNL{2}   \hspace*{.78cm}   $\pi_6\!\!:\,      $ (\LET\ \pb\  $\leftarrow$  \ldots \IN 
          \UNL{3}   \hspace*{.78cm}    $\pi_{7}\!\!:\, $(\LET\ \pw\  $\leftarrow$  (\length\ \pb) \IN~$\psi_{4}\!\!:\,$ (\RETURN\ \pw)))))))
\end{uprogram}}
        } 
    \end{boxedminipage}
    & 
    \begin{boxedminipage}{.49\textwidth}
      {\sf
        \small
        \begin{tabular}{lc}
        $\cal{M_{\mbox{\tiny \length}}} = $ 
            \begin{tabular}{lc}            
              $[$
              $\psi_2 \mapsto \lbrace \py.\epsilon, \pu.\Lf{\length}{\mbox{1}}{\epsilon}, \
              \xl.\mbox{1}\Lf{\length}{\acdr}{\epsilon}, \xl.\epsilon  \rbrace ,$ \\ 
              $\psi_1 \mapsto \lbrace \rbrace , $\\
              $\psi_3 \mapsto \lbrace \px.\epsilon, \xl.\epsilon \rbrace $  \\
              $]$
            \end{tabular} \\
            $\cal{P_{\mbox{\tiny \length}}} = [$
              \begin{tabular}{lc}
                $\pi_{\mbox{1}} \mapsto \lbrace \psi_1, \psi_2, \psi_3 \rbrace, $ \
                $ \pi_{\mbox{2}} \mapsto \lbrace \psi_1, \psi_2, \psi_3 \rbrace, $ \\
                $ \pi_{\mbox{3}} \mapsto \lbrace \psi_3 \rbrace, $ \
                $ \pi_{\mbox{4}} \mapsto \lbrace \psi_1 \rbrace, $ \
                $ \pi_{\mbox{5}} \mapsto \lbrace \psi_2 \rbrace, $ \\
                $ \pi_{\mbox{6}} \mapsto \lbrace \psi_2 \rbrace, $ \
                $ \pi_{\mbox{7}} \mapsto \lbrace \psi_2 \rbrace $ \\
                $]$
              \end{tabular}\\
              $\cal{M_{\mbox{\tiny \main}}} = $ 
              \begin{tabular}{lc}            
                $[$
                  $\psi_4 \mapsto \lbrace \pw.\sigma_{\mathit{\!all}}, \pb.\Lf{\length}{\mbox{1}}{\sigma_{\mathit{\!all}}}, \ldots  \rbrace $ \
                  $]$
              \end{tabular} \\
              $\cal{P_{\mbox{\tiny \main}}} = [$
                \begin{tabular}{lc}
                  $\pi_{\mbox{8}} \mapsto \lbrace \psi_4 \rbrace, $ \
                  $ \pi_{\mbox{9}} \mapsto \lbrace \psi_4 \rbrace, $ \\
                  $ \pi_{\mbox{10}} \mapsto \lbrace \psi_4 \rbrace, $ \
                  $ \pi_{\mbox{11}} \mapsto \lbrace \psi_4 \rbrace, $ \
                  $ \ldots  $ \
                  $]$  
                \end{tabular}
        \end{tabular}
      }
    \end{boxedminipage}
    \\
    (a) Example program.&
    \renewcommand{\arraystretch}{.9}{\begin{tabular}[t]{ll}
        (b) {\em e-path} to liveness environment map \\
        (c) Prog pt to {\em e-paths } map
    \end{tabular}}
  \end{tabular}
\end{picture}
\kern -3ex
\vspace{0.5in}
\caption{Example Program and its liveness maps.}\label{fig:mot-example2}    
\end{figure*}

@@

  \raggedright{\bf Steps:}
 %% \begin{algorithmic}
%%    \COMMENT Fix the algorithm issue
%%    %% \STATE $i \leftarrow 0$ 
%%    %% \STATE $\nt_0 \leftarrow$ Equivalent NFA of \ntbar\
%%    %% without $\epsilon$-moves \cite{hopcraft90toc}

%%    %% \REPEAT
%%    %% \STATE $\nt'_{i+1} \leftarrow \nt_i$
%%    %% \FORALL{states $q$ in $\nt_i$ such that $q$ has an incoming
%%    %%   edge from $q'$ with label $\bcar$ and
%%    %%   outgoing edge to $q''$ with label $\acar$} 
%%    %% \STATE add an edge in $\nt'_{i+1}$ from $q'$ to $q''$ with
%%    %% label $\epsilon$.
%%    %% \COMMENT{bypass  $\bcar\acar$ using $\epsilon$}
%%    %% \ENDFOR

%%    %% \FORALL{states $q$ in $\nt_i$ such that $q$ has an incoming
%%    %%   edge from $q'$ with label $\bcdr$ and outgoing edge to
%%    %%   $q''$ with label $\acdr$} 
%%    %% \STATE add an edge in $\nt'_{i+1}$ from $q'$ to $q''$ with
%%    %%   label $\epsilon$.
%%    %% \COMMENT{bypass  $\bcdr\acdr$ using $\epsilon$}
%%    %% \ENDFOR

%%    %% \STATE   $\nt_{i+1}    \leftarrow$   Equivalent   NFA   of
%%    %% $\nt'_{i+1}$ without $\epsilon$-moves

%%    %% \STATE $i \leftarrow i+1$
%%    %% \UNTIL ($\nt_{i} = \nt_{i-1}$)

%%    %% \STATE $\nt \leftarrow \nt_i$
%% %   \STATE delete all edges with label \bcar\ or \bcdr\ in \nt.
%%  \end{algorithmic}
\end{center}
\end{boxedminipage}
 \caption{Algorithm for transforming an NFA to  accept forward
   paths only.}\label{algo:simplify-NFA} \figrule
\end{figure*}
